\LARGE \bf Expectation-Maximization Based Defense Mechanism for Distributed Model Predictive Control

### 2022-05-17 article/article.tex
remove white box and capitalize title

\begin{frontmatter}
\title{\LARGE \bf
  Expectation-Maximization based defense mechanism for distributed Model Predictive Control
}

@@

          \node[draw,
          mpcSmall,
          fill=none,
          draw=white,
          below=of block1,
          ] (mult) {\vdots};

>>>>

\begin{frontmatter}
\title{\LARGE \bf
  Expectation-Maximization Based Defense Mechanism for Distributed Model Predictive Control
}

@@

          \node[draw,
          mpcSmall,
          fill=none,
          draw=none,
          below=of block1,
          ] (mult) {\vdots};
